\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-12-02 paper.qmd
Added tSNE layouts as well

@@

error_umap_plot_pbmc <- ggplot(error_pbmc, 
                               aes(x = a1, 
                                   y = MSE, 
                                   colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 13, 17, 21, 26)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

>>>>

```{r}
#| label: read-pbmc-tsne-layouts
# Read a variety of different NLDR representations of PBMC
# and plot them on same aspect ratio
tsne_pbmc1 <- read_rds("data/pbmc3k/pbmc_scdeed_tsne_perplexity_30.rds")
tsne_pbmc1 <- as_tibble(tsne_pbmc1)
names(tsne_pbmc1) <- c("tSNE1", "tSNE2")

nldr1c <- tsne_pbmc1 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2)) +
  geom_point(alpha=0.1, size=1, colour='#e41a1c') +
  interior_annotation("a")

tsne_pbmc2 <- read_rds("data/pbmc3k/pbmc_scdeed_tsne_perplexity_320.rds")
tsne_pbmc2 <- as_tibble(tsne_pbmc2)
names(tsne_pbmc2) <- c("tSNE1", "tSNE2")

nldr2c <- tsne_pbmc2 |>
  ggplot(aes(x = tSNE1,
             y = tSNE2))+
  geom_point(alpha=0.1, size=1, colour='#377eb8') +
  interior_annotation("b")

```{r}
#| label: combine-data-pbmc-tsne

error_pbmc_tsne <- read_rds("data/pbmc3k/error_scdeed_pbmc_tsne_perplexity_30.rds")
error_pbmc_tsne2 <- read_rds("data/pbmc3k/error_scdeed_pbmc_tsne_perplexity_320.rds")

error_pbmc <- bind_rows(error_pbmc_tsne, 
                        error_pbmc_tsne2)

```{r}
#| label: error-comp-pbmc-tsne

error_tsne_plot_pbmc <- ggplot(error_pbmc, 
                               aes(x = a1, 
                                   y = MSE, 
                                   colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 12, 15, 17, 19, 21)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

```{r}
#| label: fig-pbmc-mse-tsne
#| fig-pos: H
#| out-height: 100%

free(error_tsne_plot_pbmc) + wrap_plots(nldr1c, nldr2c, ncol = 2)
```

@@

error_umap_plot_pbmc <- ggplot(error_pbmc, 
                               aes(x = a1, 
                                   y = MSE, 
                                   colour = method)) + 
  geom_point(size = 0.8) +
  geom_line(linewidth = 0.3) + 
  # geom_vline(xintercept = 15, linetype="solid", 
  #            color = "black", linewidth=0.8, alpha = 0.5) +
  scale_x_continuous(breaks = sort(unique(error_pbmc$a1))[c(1, 5, 9, 12, 15, 17, 19)]) +
  scale_color_manual(values=c('#e41a1c','#377eb8')) +
  scale_y_log10() +
  ylab("log(MSE)") +
  xlab(expression(paste("binwidth (", a[1], ")"))) +
  theme_minimal() +
  theme(panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line(),
        legend.position = "none",
        axis.text.x = element_text(size = 7),
        axis.text.y = element_text(size = 7),
        axis.title.x = element_text(size = 7),
        axis.title.y = element_text(size = 7))

### 2024-12-02 paper.tex
Added tSNE layouts as well

@@

\begin{center}
\includegraphics[width=0.5\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-65-1.pdf}
\end{center}

>>>>

\includegraphics[width=1\textwidth,height=1\textheight]{paper_files/figure-pdf/fig-pbmc-mse-tsne-1.pdf}

\caption{\label{fig-pbmc-mse-tsne}}

@@

\begin{center}
\includegraphics[width=0.5\textwidth,height=\textheight]{paper_files/figure-pdf/unnamed-chunk-69-1.pdf}
\end{center}
